*Bromus* Initial Analysis

### 2019-07-23 Scripts/BromusUpdate.Rmd
Checking for LaTeX installation

---
title: "*Bromus* Initial Analysis"
author: "Nick Gotelli"
date: "7/19/2019"
output: 
  html_document: 
    highlight: tango
    theme: cerulean
---

>>>>

---
title: '*Bromus* Initial Analysis'
author: "Nick Gotelli"
date: "7/19/2019"
output:
  pdf_document: default
  html_document:
    highlight: tango
    theme: cerulean
---
